Model Samples Processing

### 2020-01-21 stats/model.Rmd
update model output processing

model_pred <- read_csv("../saves/model/samples78.csv") %>%
  filter(a == "modelPrediction")%>%
  select(-a)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         id = f,
         item = e,
         age = g, 
         pred = h)

saveRDS(model_pred, "../saves/model_pred.rds")
model_pred <- readRDS("../saves/model_pred.rds")

model_params <- bind_rows(
  readRDS("../saves/model_params_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_params_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/model_params_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/model_params_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/model_params_chain5.rds")%>%mutate(chain = 5)

)

item_params <-  model_params %>%
  filter(b == "items")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(item = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

global_params <- model_params %>%
  filter(b == "parameters")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

global_sigma<- model_params %>%
  filter(b == "sigma")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

@@

model_pred %>%
  filter(item == "pawn")%>%
  arrange(age)
```
## Plotting model parameters

>>>>

model_pred <- readRDS("../saves/model_pred.rds")

item_params <- readRDS("../saves/item_params.rds")

global_params <- readRDS("../saves/global_params.rds")

global_sigma <- readRDS("../saves/global_sigma.rds")

@@

```
## Plotting model parameters

### 2020-01-21 stats/model_sample_processing.Rmd
update model output processing

# Read in raw filed

@@

model <- bind_rows(
  read_csv("../saves/model/samples340.csv")%>%mutate(chain = 1),
  read_csv("../saves/model/samples561.csv")%>%mutate(chain = 2)
)

@@

# Model predictions
```{r}
model_pred <- model %>%
  filter(a == "modelPrediction")%>%
  select(-a)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         id = f,
         item = e,
         age = g, 
         pred = h)

saveRDS(model_pred, "../saves/model_pred.rds")
model_pred <- readRDS("../saves/model_pred.rds")
```

@@

```{r}
item_params <-  model %>%
  filter(b == "items")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(item = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

global_params <- model %>%
  filter(b == "parameters")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

global_sigma<- model %>%
  filter(b == "sigma")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)
```

>>>>

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
library(langcog)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

# Read in raw file

@@

model <- bind_rows(
  read_csv("../webppl/output/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
  read_csv("../saves/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
)

@@

# Model predictions

```{r}
model_pred <- model %>%
  filter(a == "modelPrediction")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred, "../saves/model_pred.rds")

@@

```{r}
item_params <-  model %>%
  filter(b == "items")%>%
  select(-a,-b, -e, -f, -h)%>%
    rename(item = c,
         parameter = d,
         value = g)

saveRDS(item_params, "../saves/item_params.rds")

global_params <- model %>%
  filter(b == "parameters")%>%
  select(-a,-b, -e,-f, -h)%>%
    rename(parameter = c,
         type = d,
         value = g)

saveRDS(global_params, "../saves/global_params.rds")

global_sigma<- model %>%
  filter(b == "sigma")%>%
  select(-a,-b, -e,-f,-h)%>%
    rename(parameter = c,
         type = d,
         value = g)

saveRDS(global_sigma, "../saves/global_sigma.rds")
```
